Differential Testing Runtime Engines--Lessons Learned from the JavaScript Domain

### 2018-07-13 paper/paper.tex
minor fixes

\section{ES6 design}
\label{sec:es6-design}
The EcmaScript is a language specification maintained by 
a committee called TC39 (Technical Committee) that follows 
standard rules proposed by ISO/ETC JTC 1 - 
Information Technology since 1996~\cite{es6-website}.
The latest version of EcmaScript commonly called ES6

\Fix{to appear}

@@

The infrastructure outputs a list of warnings for human inspection.
To reduce the number of false alarms, we clustered warnings in two
groups, reflecting their likelihood to manifest a real bug. Warnings
in the HI group are associated with the cases when the anomaly has been
detected during the execution of the test code or its close neighborhood\Comment{ as
  opposed to that of some internal JS function}, crashes (ie. FatalError) and core dumps 
  are considered HI group as well. The rationale is that
the test in this group executed without violating any internal checks
of the API. In constrast, warnings in the LO group reflect the cases where the
anomaly was observed during the execution of functions from standard JS
libraries. For example, according to the latest version of ES6 specification\cite{es6-spec},
they
\Mar{what is that exactly? can we cite? is that only spec or
actually code as most of java.* libraries.}
We found that different engines often check pre-conditions of those
functions differently. It can happen, for example, that one engine
enforces a weaker pre-condition compared to another.
% \Mar{why is that?
% that should not happen if the spec was fully documented and engines
% properly implemented those checks. Explain and give example.}
\Igor{these cases happen because the specification describes how a function
should work, however the internal implementation is defined by the
engine developers}\Mar{If you confirm that there is no code in specs
  (see comment above), what would be those abstract
  functions/interfaces that you mentioned to me the other day?}.
\Igor{In addiction, we inserts in LO groups tests that generates a timeout warning
due the capacity of a fuzzer add an infinite repetition statement. We expected that
each test process can running utmost 5 seconds, if exceed this condition we stop 
the process and add a output message of a TIMEOUT error.}
In those cases,
our infrastructure would observe a discrepancy that is more likely to
be associated with a bug in the (fuzzed) test; not the code. Although
we did find real bugs from warnings in the LO group, the proportion
was much lower compared to the HI group--only 12\% of the reals bugs
we found originated from the LO category. \Mar{show real examples of
  HI and LO. Use the stacktraces to explain what is going on.}

@@

\begin{figure}[h!]
  \centering
  \scriptsize
  \lstset{escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c,
    numberstyle=\tiny,
    morekeywords={assertEq, var, yield, in, function, 
    typeof, return, throw, new, Error, if},
  }
  \begin{lstlisting}
seeds/Duktape/ecma_fixed/test-dev-bound-func-many-args.js:4: Error: Test Failed
throw new Error("Test Failed");
  ^
Error: Test Failed
  at String.target (seeds/Duktape/ecma_fixed/test-dev-bound-func-many-args.js:4:13)
  at seeds/Duktape/ecma_fixed/test-dev-bound-func-many-args.js:23:1
\end{lstlisting}
\normalsize
\caption{Warning captured as HI priority.}
\label{fig:hi-priority}
\end{figure}

\begin{figure}[h!]
  \centering
\begin{minipage}{.45\textwidth}
  \scriptsize
  \lstset{escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c,
    numberstyle=\tiny,
    morekeywords={assertEq, var, yield, in, function, 
    typeof, return, throw, new, Error, if},
  }
  \begin{lstlisting}[caption=JavaScript code fuzzed by radamsa,frame=tlrb]{Name}
  void code()
  {

  }
  \end{lstlisting}
  \end{minipage}\vfill
  \begin{minipage}{.45\textwidth}
    \scriptsize
    \lstset{escapeinside={@}{@},
      numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
      basicstyle=\ttfamily\scriptsize, boxpos=c,
      numberstyle=\tiny,
      morekeywords={assertEq, var, yield, in, function, 
      typeof, return, throw, new, Error, if},
    }
  \begin{lstlisting}[caption=Console Output,frame=tlrb]{Name}
  void code()
  {

  }
  \end{lstlisting}
  \end{minipage}
  \caption{Warning captured as HI priority.}
  \label{fig:lo-priority}
\end{figure}

@@

Table~\ref{tab:test-suites} shows the JS sources we considered for
each of the selected projects. Overall, we found a total of
\totfiles{} JS files. It is worth noting that some projects use
distinct frameworks for testing and require external libraries to run
their testing suites. For these projects, we needed to make small
changes in the testing infrastructure to be able to uniformly run
tests in all engines.\Mar{not entirely clear what you did to support
  this.$\rightarrow$}\Igor{wip}\Mar{apenas explique o que fez (mesmo
  que em portugues). isto nao deveria levar tempo que justifique
  escrever wip.}We aimed to use only the JS file with minor fixes to
support our environment. These fixes are composed by an assertion
function that throws an Error that we can capture by our
infraestruture.

>>>>

\section{ES6 design}
\label{sec:es6-design}
The EcmaScript is a language specification maintained by 
a committee called TC39 (Technical Committee) that follows 
standard rules proposed by ISO/ETC JTC 1 - 
Information Technology since 1996~\cite{es6-website}.
Along the year, a new version of EcmaScript (the latest version is ES2017) adds
new features and minor fixes for the language. \Fix{discutir mais sobre isso}

@@

The infrastructure outputs a list of warnings for human inspection.
To reduce the number of false alarms, we clustered warnings in two
groups, reflecting their likelihood to manifest a real bug. Warnings
in the HI group are associated with the cases when the anomaly has been
detected during the execution of the test code or its close neighborhood\Comment{ as
  opposed to that of some internal JS function}, crashes (ie. FatalError) and core dumps 
  are considered HI group as well. The rationale is that
the test in this group executed without violating any internal checks
of the API. In constrast, warnings in the LO group reflect the cases where the
anomaly was observed during the execution of functions from standard JS
libraries.
\Mar{what is that exactly? can we cite? is that only spec or
actually code as most of java.* libraries.}
We found that different engines often check pre-conditions of those
functions differently. It can happen, for example, that one engine
enforces a weaker pre-condition compared to another.
% \Mar{why is that?
% that should not happen if the spec was fully documented and engines
% properly implemented those checks. Explain and give example.}
\Igor{these cases happen because the specification describes how a function
should work, however the internal implementation is defined by the
engine developers}\Mar{If you confirm that there is no code in specs
  (see comment above), what would be those abstract
  functions/interfaces that you mentioned to me the other day?}.
For example, the latest version of ES specs~\cite{es6-spec} describes that,
the function \CodeIn{Number.toPrecision(precision)}, in general,
returns a String containing the Number value represented either 
in decimal exponential notation or in decimal fixed notation, 
if precision is defined~\cite{es6-toPrecision}. The Number object uses a 
property called

\Igor{In addiction, we inserts in LO groups tests that generates a timeout warning
due the capacity of a fuzzer add an infinite repetition statement. We expected that
each test process can running utmost 5 seconds, if exceed this condition we stop 
the process and add a output message of a TIMEOUT error.}
In those cases,
our infrastructure would observe a discrepancy that is more likely to
be associated with a bug in the (fuzzed) test; not the code. Although
we did find real bugs from warnings in the LO group, the proportion
was much lower compared to the HI group--only 12\% of the reals bugs
we found originated from the LO category. \Mar{show real examples of
  HI and LO. Use the stacktraces to explain what is going on.}

@@

\begin{figure}[h!]
  \centering
  \scriptsize
  \lstset{escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c,
    numberstyle=\tiny,
    morekeywords={assertEq, var, yield, in, function, 
    typeof, return, throw, new, Error, if},
  }
  \begin{lstlisting}
\end{lstlisting}
\normalsize
\caption{Warning captured as LO priority.}
\label{fig:hi-priority}
\end{figure}

@@

Table~\ref{tab:test-suites} shows the JS sources we considered for
each of the selected projects. Overall, we found a total of
\totfiles{} JS files. It is worth noting that some projects use
distinct frameworks for testing and require external libraries to run
their testing suites. For these projects, we needed to make small
changes in the testing infrastructure to be able to uniformly run
tests in all engines.\Mar{not entirely clear what you did to support
  this.$\rightarrow$}\Mar{apenas explique o que fez (mesmo
  que em portugues). isto nao deveria levar tempo que justifique
  escrever wip.}We aimed to use only the JS file with minor fixes to
support our environment. These fixes are composed by an assertion
function that throws an Error that we can capture by our
infraestruture.
